Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System

### 2022-12-10 paper-kelompok/main.tex

\section{Conclusions}
To support the study of spectrophotometry analysis in DMF platform, we have proposed the assembly of a portable visible spectrophotometer that can be integrated with a particular DMF system.
Data acquisition, storage, and user experience is made simpler by our developed portable visible spectrophotometer and a user-friendly interface.
Measurement's accuracy of red, yellow, and blue food dyes and its repeatability demonstrated good performances in experimental validation versus commercial spectrophotometer (Thermo Scientific™ Evolution 220).
The colorimetric glucose assay (maximum of absorbance at 540 nm) measurements were comparable but quite inferior; these issues could be resolved by retesting the colorimetric reactions more thoroughly.
Future work will focus on designing a better voltage regulation and heat insulation for the lamp, as well as reducing movable parts from the light path configuration.

>>>>

\section{Conclusions}
To support the study of spectrophotometry analysis in DMF platform, we have proposed the assembly of a portable visible spectrophotometer that can be integrated with a particular DMF system.
Data acquisition, storage, and user experience is made simpler by our developed portable visible spectrophotometer and a user-friendly interface.
Measurement's accuracy of red, yellow, and blue food dyes and its repeatability demonstrated good performances in experimental validation versus commercial spectrophotometer (Evolution 220 UV-Visible, Thermo Scientific™).
The colorimetric glucose assay (maximum of absorbance at 540 nm) measurements were comparable but quite inferior; these issues could be resolved by retesting the colorimetric reactions more thoroughly.
Future work will focus on designing a better voltage regulation and heat insulation for the lamp, as well as reducing movable parts from the light path configuration.
